InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-23 paper.tex
Remove double whitespace
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

@@

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

>>>>

Another tool to automatically detect generated text is \textbf{GLTR}. It applies different baseline statistical methods to detect generation artifacts. To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated. The text is compared with the distribution of next words, in the given context. The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context. If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g. the currently hosted GPT2 117M model. Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model. This approach can also be used for other models. \cite{gehrmann-etal-2019-gltr}

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released. The model is limited to english texts only and is openly available under the MIT license.

@@
